---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# beginr

<!-- badges: start -->
<!-- badges: end -->

The goal of `beginr` is to make it a bit easier to learn R.
It provides convenience functions and example datasets to make some common tasks a bit easier.

## Installation

You can install the development version of `beginr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mjgreen/beginr")
```

## Usage

Generate the `dat_long` data using the command `manufacture_ldt_long_data()`

```{r, show_manufacture_function_howto}
library("beginr")
dat_long <- manufacture_ldt_long_data()
dat_long
```

See that the data set is in the right form for `ggplot`

```{r, plotDensityByCondition}
require("ggplot2")
ggplot(dat_long, aes(x = rt, fill = condition)) +
  geom_density(alpha = 0.75)+
  scale_x_continuous(name = "Reaction time (ms)")+
  scale_fill_discrete(name = "Condition")
```

